Full Brain Blood-Oxygen-Level-Dependent Signal Parameter Estimation Using Particle Filters

### 2010-08-25 doc/paper/main.tex
results all in

%todo fix these histograms with marker for true value and drop A1,A2
\begin{figure*}[!t] %top left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=15cm]{images/slicesim_hist2}
\caption{Histogram of estimated parameters. Average SNR in the region was 
$0.97$ and Mutual Information between simulation and BOLD estimate was greater 
than $0.15$.}
\label{fig:slicesim_hist2}
\end{figure*}

\begin{figure*}[!t] %top left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=15cm]{images/slicesim_hist3}
\caption{Histogram of estimated parameters for region 3. Average SNR in the 
region was 
$0.39$ and Mutual Information between simulation and BOLD estimate was greater 
than $0.15$.}
\label{fig:slicesim_hist3}
\end{figure*}

@@

\subsection{Real Data}
\begin{figure*}
\centering
\subfigure[]{\label{fig:hm_spm} \includegraphics[scale=.85]{images/spm_hm}}
\subfigure[]{\label{fig:hm_canon_spm_x} \includegraphics[scale=3]{images/spm_hm_x}}
\subfigure[]{\label{fig:hm_canon_spm_y} \includegraphics[scale=3]{images/spm_hm_y}}
\subfigure[]{\label{fig:hm_canon_spm_z} \includegraphics[scale=3]{images/spm_hm_z}}
\subfigure{\label{fig:scale_spm} \includegraphics[scale=.5]{images/scale1}}
\caption{SPM results. Units of activation are in Student's $t$-scores; higher indicates higher
        assurance that the signal cannot have occurred through noise alone.
        Sagittal, coronal and axial slices  are
        \autoref{fig:hm_canon_spm_x}, \autoref{fig:hm_canon_spm_y}, and
         \autoref{fig:hm_canon_spm_z}, respectively. A series of axial slices are
         shown in \autoref{fig:hm_spm}. }
\label{fig:hm_canon_spm}
\end{figure*}

@@

\begin{itemize}
\item Parameters ill-defined
\end{itemize}

>>>>

%todo fix these histograms with marker for true value and drop A1,A2
\begin{figure*}[!t] %top left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=15cm]{sec2hist}
\caption{Histogram of estimated parameters. Average SNR in the region was 
$0.97$ and Mutual Information between simulation and BOLD estimate was greater 
than $0.15$.}
\label{fig:slicesim_hist2}
\end{figure*}

\begin{figure*}[!t] %top left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=15cm]{sec3hist}
\caption{Histogram of estimated parameters for region 3. Average SNR in the 
region was 
$0.39$ and Mutual Information between simulation and BOLD estimate was greater 
than $0.15$.}
\label{fig:slicesim_hist3}
\end{figure*}

@@

\subsection{Real Data}
\begin{figure*}
\centering
\subfigure{\label{fig:hm_spm} \includegraphics[scale=3]{spm_hm}}
\subfigure{\label{fig:scale_spm} \includegraphics[scale=.35]{scale1}}
\caption{SPM results. Units of activation are in Student's $t$-scores; higher indicates higher
        assurance that the signal cannot have occurred through noise alone.}
\label{fig:hm_canon_spm}
\end{figure*}

\begin{figure*}
\centering
\subfigure{\label{fig:hm_mi} \includegraphics[scale=3]{hm_mi_strict}}
\subfigure{\label{fig:scale_mi} \includegraphics[scale=.35]{scale4}}
\caption{Particle filter results. Units of activation are in mutual information; higher
    indicates more assured activation.}
\label{fig:hm_canon_spm}
\end{figure*}

The result of real experiments concentrates on regions of activation, because
of the significant possiblity that the parameters are strictly defined. The
quality of fit used for the particle filter results is mutual information which
in preliminary testing showed fewer false positives than normalized Mean Squared
Error.

@@
